\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{tikz}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
        }
    }

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape Mirco Mazzoni} \\ \vspace{1pt}
    \small +39-351-555-9888 $|$ \href{mailto:mirco.mazzoni.03@gmail.com}{\underline{mirco.mazzoni.03@gmail.com} \ExternalLink} $|$ 
    \href{https://www.linkedin.com/in/mirco-mazzoni-022816219/}{\underline{linkedin.com/in/mirco} \ExternalLink} $|$
    \href{https://github.com/Penca53}{\underline{github.com/Penca53} \ExternalLink}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
     \resumeSubheading
      {University of Genoa}{Genoa, IT}
      {Bachelor Degree in Computer Science}{Sep. 2022 -- Aug. 2025}
      \resumeSubheading
      {ITIS Ferraris-Pancaldo}{Savona, IT}
      {High School Diploma in Computer Science - Grade 100/100 cum laude}{Sep. 2017 -- Jun. 2022}
     \resumeSubheading
      {\href{https://cyberchallenge.it/halloffame/2021}{CyberChallenge.IT \ExternalLink}}{Genoa, IT}
      {National project for CyberSecurity training - 3rd place in national CTF competition}{Feb. 2021 -- Aug. 2021}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Developer Internship}{May 2021 -- Aug. 2021}
      {CodeDay Labs}{}
      \resumeItemListStart
        \resumeItem{Developed an "Inventory Manager" full-stack web application using React and SpringBoot to serve multiple REST APIs, deployed on the AWS infrastructure, leading to an average 40\% speed increase in inventory management for shops and warehouses}
        \resumeItem{Implemented continuous delivery using GitHub CI/CD Actions to build and scan (with SonarCloud) the application upon a new release, speeding up the testing phase by 70\% and the overall deployment process by 50\% }
      \resumeItemListEnd
    \resumeSubHeadingListEnd

 %-----------AWARDS AND ACHIEVEMENTS-----------
\section{Awards \& Achievements}
  \resumeSubHeadingListStart
     \resumeSubheading
      {\href{https://www.linkedin.com/company/leadthefuture/mycompany/}{Lead The Future Mentee \ExternalLink}}{}
      {LeadTheFuture is a leading mentorship for students in STEM, with an acceptance rate below 20\%}{Sep. 2022 -- Present}
      \resumeSubheading
      {Silver Medal - Italian Olympiad in Informatics}{}
      {Top 0.5\% among all participants}{Nov. 2021}
  \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{{\href{https://github.com/Penca53/aubengine}{{Game Engine} \ExternalLink}}} $|$ \emph{C++, OpenGL}}{Sep. 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Developing a cross-platform game engine based on the OpenGL rendering API, keeping a hot-swap modular structure to allow future implementations and ease code expandability by 30\%}
            \resumeItem{Implemented a high-level networking library (TCP and UDP) based on ASIO, allowing the creation of server authoritative real-time multiplayer games and supporting snapshot synchronization}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Localization Editor} $|$ \emph{C\#, XAML, WPF}}{Nov. 2020 -- Jan. 2021}
          \resumeItemListStart
            \resumeItem{Developed a desktop app to ease the creation and the management of localization files, speeding up the overall translation process of professional applications by 65\%}
            \resumeItem{Implemented a versioning system that allows the application to recognize and report old or obsolete translations}
            \resumeItem{Implemented a retro-compatibility system to maintain and adapt previous localization files}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Database Editor} $|$ \emph{C\#, XAML, WPF}}{May 2020 -- Jul. 2020}
          \resumeItemListStart
            \resumeItem{Developed a desktop app to create, edit and export custom file-based databases}
            \resumeItem{Implemented an intuitive spreadsheet view that allows easy and quick edits in tables and data types}
            \resumeItem{Improved CPU and memory usage by 83\% adding column virtualization to the main table view}
          \resumeItemListEnd
      \resumeProjectHeading
          {{\textbf{{\href{https://konstantin890.itch.io/steven-the-cat}{{Steven The Cat - 2D Game} \ExternalLink}}} $|$ \emph{C\#, Unity, Aseprite}}}{Sep. 2019}
          \resumeItemListStart
            \resumeItem{Developed a game submission for a 7-day long GameJam, receiving an average 4.5/5-star review \newline
            and scoring 30th over 4000 participants}
            \resumeItem{Implemented world map physics and player controller following a component-based structure, allowing full code reusability that increased productivity by over 50\%}
            \resumeItem{Collaborated with a team on a constant improvement of the game development process to maximize efficiency and ship a MVP in the shortest possible time - 25\% gain in efficiency}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C\#, C/C++, Java, Go, PHP, Python, JavaScript/TypeScript, HTML/CSS, XAML, SQL (Postgres)} \\
     \textbf{Frameworks and Engines}{: React, Vue, Svelte, Angular, Node.js, Electron, Tauri, WPF, SpringBoot, FastAPI, Gin, ASP.NET, Unity, OpenGL, Docker, MSTest, JUnit, OpenAPI, Swagger} \\
     \textbf{Developer Tools}{: Git, VS Code, Visual Studio, IntelliJ, Eclipse, Docker, AWS, CI/CD Actions, Trello, Jira}
    }}
 \end{itemize}
\end{document}
